Neural Style Transfer on Text\\Project Report One

### 2017-10-29 dl-style-transfer/reports/src/project_report_one.tex
FIxed name
Update project_report_one.tex

\author{Yuji Akamoto, Ryan Butler, Cameron Ibrahim, Luca Leeser}

@@

	\item [Yuji Akamoto]
		Created a CNN for text representation.

@@

>>>>

\author{Yuji Akimoto, Ryan Butler, Cameron Ibrahim, Luca Leeser}

@@

	\item [Yuji Akimoto]
		Implemented image style transfer with VGG-16 trained on CIFAR-10 data instead of ImageNet data, to see if ``content'' representations of images would still be general enough. Also implemented (untrained) ``Shallow-CNN'', a popular convolutional architecture for text classification as described by [Yoon Kim](https://arxiv.org/abs/1408.5882).

@@

	\bibitem{Shallow-CNN}
	Yoon Kim.
	\textit{Convolutional Neural Networks for Sentence Classification}. CoRR, 2014.
